The pollination trade-off

### 2018-11-22 paper/manuscript.Rmd
Add pca variable contribution to manuscript

  # cowplot::plot_grid(
  #   slopes_plot, 
  #   drake::readd(fig_con_con),
  #   drake::readd(fig_con_hetero_gain), 
  #   ncol = 1, 
  #   rel_heights = c(1/2, 1/2, 1/4))

```

>>>>

```{r strategy-fig-height}
height0 <- 1.55
height1 <- 2.7
height2 <- 2.4
strategy_fig_height <- sum(height0, height1, height2)
```

```{r, fig.width=3.25, fig.height=strategy_fig_height, fig.cap="PCA results."}
# fig_pca <- plot_pca(pcas, chosen_threshold = 0)
# fig_distances <- plot_permanova_dist(permanova_plant_distances, permanova_site_distances)
# fig_pca_contrib <- plot_pca_variances_and_contributions(pcas, chosen_threshold = 0)
# pdf(width = 3.25, height = strategy_fig_height)
drake::loadd(fig_pca_contrib)
drake::loadd(fig_pca)
drake::loadd(fig_distances)
cowplot::plot_grid(
  fig_pca_contrib,
  fig_pca, 
  fig_distances,
  ncol = 1, 
  rel_heights = c(height0, height1, height2), 
  align = "v"
)
# dev.off()
```
